### 2020-12-21 LaTeX-USENIX/sections/paper.tex
PQ insertion figure added
edits

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{fig/random_insertion2.png}
\caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants. For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue. The y-axis is the cost of enqueuing in gas.}  \label{fig:random_insertion}}
\end{figure}

@@

@@

\paragraph{Front-running.} The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.

@@

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.5\textwidth]{fig/random_insertion3.png}
\caption{\footnotesize{Gas costs for enqueuing 50 random integers into five priority queue variants. For the x-axis, a value of 9 indicates it is the 9th integer entered in the priority queue. The y-axis is the cost of enqueuing in gas.}  \label{fig:random_insertion}}
\end{figure}

@@

\textblue{Reviewer's comment: DDOS against submitbid and submitask functions. Our answer: we put a cap on the number of orders submitted to the market so that we can always close. Also talk about bulk displacement attack (see reviewers comments)}

@@

\paragraph{Front-running.} \textblue{we have to revisit this section: talk about our front-running paper: there are various ways to prevent frontrunning, one is through confidentiality..., then cite this paper: 'TEX – A Securely Scalable Trustless Exchange'~\cite{khalil2019tex} }The primary motivation for using a call market, as opposed to a continuous-time order book, is to mitigate front-running attacks~\cite{clark2014decentralizing,eskandari2019sok,daian2019flash}. Consider a sequence of 100 orders submitted within a window of time to market A, and the same sequence is randomly shuffled and submitted to market B. If A and B are continuous, the orders that are executed in A could be quite different from B. In a call market, the outcome of A and B will be exactly equivalent. There is no threat from miners reordering transactions or traders offering higher gas rates to have their orders executed before other orders already broadcasted.

@@

 \textblue{ We need to find a home for this: another solution to reopen the market immediately after the closing call is to have many similar contracts for the market and  a factory contract to guide users to the correct address (from the reviewer's comment)}
